Methods for Large Scale Learning to Rank

### 2014-07-17 report/Chapters/Implementation.tex
nieuwe lineare regressie voor SmoothRank

Describes implementation details of the Learning-to-Rank algorithm parallel implementations in HDInsight that are either Hadoop, Microsoft Azure, or HDInsight and are not part of the algorithm specification itself.

>>>>

This chapter describes implementation details of the Learning-to-Rank algorithm parallel implementations in HDInsight that are either Hadoop, Microsoft Azure, or HDInsight and are not part of the algorithm specification itself. The first section of this chapter will briefly discuss the HDInsight platform, the Hadoop ecosystem components offered by HDInsight and, in this regard, the Hadoop components used for implementation of the algorithms described in Chapter \ref{chap:ltr_methods}.

\section{The HDInsight platform}
TODO:
 - No direct access to jobtracker
 - C# API and access via Windows PowerShell scripts
 - REST endpoints for Templeton/WebHcat / Ambari / HiveServer / HiveServer2 and Oozie
 - Pig for ease of implementation
 - Templeton and Oozie allow submission of Pig jobs
 - Oozie requires Pig jobs to be stored on HDFS, Templeton allows running dynamically generated Pig from code.

\section{Algorithm implementation}
\subsection{ListNet}

### 2014-07-17 report/Chapters/LTRMethods.tex
nieuwe lineare regressie voor SmoothRank

The learning algorithms of the well-performing Learning-to-Rank methods selected in Chapter \ref{chap:cross_comparison} are presented and explained in this Chapter. The Learning-to-Rank methods will be discussed in order of an increasing degree of certainty and decreasing ranking accuracy, as concluded in Chapter \ref{chap:cross_comparison}.

>>>>

\label{chap:ltr_methods}
The learning algorithms of the well-performing Learning-to-Rank methods selected in Chapter \ref{chap:cross_comparison} are presented and explained in this Chapter. The Learning-to-Rank methods will be discussed in order of an increasing degree of certainty and decreasing ranking accuracy, as concluded in Chapter \ref{chap:cross_comparison}.
